Final Project Code ALL

### 2022-12-10 ClusteringModel.Rmd
checked some things

@@

>>>>

# Select the variables to be used in clustering
imdb_hc_sub <- imdb_hc %>%
    select(Budget, Runtime)

@@

```{r}
# Random subsample of 25 Movies
set.seed(253)

imdb_hc <- imdb_clean %>%
    slice_sample(n = 25)

imdb_hc_full1 <- imdb_clean %>%
  select(Gross, Budget)

imdb_hc_full2 <- imdb_clean %>%
  select(Budget, Runtime)

# Compute a distance matrix on the scaled data
dist_mat_scaled <- dist(scale(imdb_hc_sub))     # Subset Distance Matrix

dist_mat_full1 <- dist(scale(imdb_hc_full1))      # Full Data Distance Matrix
dist_mat_full2 <- dist(scale(imdb_hc_full2))      # Full Data Distance Matrix
```

### Create Clusters

```{r}
imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
imdb_full_avg1 <- hclust(dist_mat_full1, method = "average")    # Full Data
imdb_full_avg2 <- hclust(dist_mat_full2, method = "average")    # Full Data
```

### Cutting the Tree

```{r}
one_imdb_clean <- imdb_clean %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg1, k = 3)) # Cut into 6 clusters (k)
    )

two_imdb_clean <- imdb_clean %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg2, k = 2)) # Cut into 6 clusters (k)
    )
```

### Visualizing Genres in Final Clusters (Full Data)

```{r}
ggplot(one_imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(two_imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(one_imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(two_imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()
```

### 2022-12-10 Draft_Final_Code.Rmd
checked some things

ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
  geom_point() + theme_classic()

@@

ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()
```

>>>>

ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
  geom_point() + 
  labs(x = "Budget", y = "Log(Gross)") +
  theme_classic()

@@

ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()

imdb_clean %>%
  count(hclust_num)
```
